Effects of CHILDREN's programs

### 2020-02-24 paper.Rnw

fundamental_dynamics <- xtable(fundamental_dynamics,
                               digits = c(0, 0, 1, 1, 0, 0),
          caption = "Summary Statistics",
          align = "lmmmmm"
          )
print(fundamental_dynamics, include.rownames = FALSE)
@
% look up official names of price indices in English 
At the beginning of the time series in 2011, they supported in x institutions. In 2018, this number had increased to y. In this section, we give an overview of the dynamics of CHILDREN's two flagship programs. We focus on the number of estimated ultimate beneficiaries, median total subsidy, median subsidy per institution, and median subsidy per beneficiary. We also look at selected outcomes, i.e. those related to health as well as self-worth and day-to-day skills. We have converted all nominal monetary variables into 2015 euros, using price indices from the Federal Statistical Office of Germany (Statistisches Bundesamt). We deflate (requested) grants as well as organizations' total expenses for the Meals program  with the price index related to food and non-alcoholic beverages (in German: Nahrungsmittel und alkoholfreie Getränke) and (requested) grants towards the Trips program with the price index for leisure, entertainment, and culture (in German: Freizeit, Unterhaltung und Kultur). These are only available after logging in on DESTATIS. The organizations also gave information about their total yearly budget. We inflate this with the general price index.

@@

@@

>>>>

fundamental_dynamics <- xtable(fundamental_dynamics,
                               digits = c(0, 0, 1, 1, 0, 0),
          caption = "Summary Statistics",
          align = "lmmmmm"
          )
print(fundamental_dynamics, include.rownames = FALSE)
@
% look up official names of price indices in English

At the beginning of the time series in 2011, they supported in x institutions. In 2018, this number had increased to y. In this section, we give an overview of the dynamics of CHILDREN's two flagship programs. We focus on the number of estimated ultimate beneficiaries, median total subsidy, median subsidy per institution, and median subsidy per beneficiary. We also look at selected outcomes, i.e. those related to health as well as self-worth and day-to-day skills. We have converted all nominal monetary variables into 2015 euros, using price indices from the Federal Statistical Office of Germany (Statistisches Bundesamt). We deflate (requested) grants as well as organizations' total expenses for the Meals program  with the price index related to food and non-alcoholic beverages (in German: Nahrungsmittel und alkoholfreie Getränke) and (requested) grants towards the Trips program with the price index for leisure, entertainment, and culture (in German: Freizeit, Unterhaltung und Kultur). These are only available after logging in on DESTATIS. The organizations also gave information about their total yearly budget. We inflate this with the general price index.

@@

\section{Regressions}

<<Grants Regressions, echo=FALSE, results='asis', message=FALSE>>=

lm_ms = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")

stargazer(lm_ms, lm_ts, title = "Regression outcome: Grants", align = TRUE)  
@
<<Health Regressions, echo=FALSE, results='asis', message=FALSE>>=

#scaled regressions

lm_lDGE = readRDS("./ANALYSIS/Tables/lessIll_DGE_scaled.lm.Rds")
lm_dDGE = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_scaled.Rds")
lm_aDGE = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_scaled.Rds")

#expanded model less ill

lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")

stargazer(lm_lDGE, lm_dDGE, lm_aDGE, title = "Regression outcome: Health", align = TRUE)
@
<<Chance Equality Regressions, echo=FALSE, results='asis', message=FALSE>>=

lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
lm_ss = readRDS("./ANALYSIS/Tables/selfworth_scaled.Rds") #standardized
lm_ds = readRDS("./ANALYSIS/Tables/dayToDaySkills_scaled.lm.Rds") #standardized

stargazer(lm_s, lm_d, lm_ss, lm_ds, title = "Regression outcome: Chance Equality", align = TRUE)
@

@@

\section{Factor Analysis}

\section{Appendix}

A1\\ 
Cumulative Odds Regression 
Outliers?

#read in data from vglm models

@

A2\\
Partition

In addition to the factor analysis described in section 6, we would like to introduce to a another dimensionality reduction method called partition.

QUOTES FROM PAPER, describe method

In the following a threshold of 0.4 is used, meaning that the reduced variable consists of variables which explain each other to at least 40 percent. It might be meaningful to decide to use only one of the variables a reduced variable consists of or a summarizing one for future surveys to avoid redundancy. Table x shows the obtained results of the dimensionality reduction and displays x variables which haven't been reduced, and x reduced ones.

<<Partition, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=

partition_meals = readRDS("./ANALYSIS/Tables/PartitionMeals.4.Rds")
partition_trips = readRDS("./ANALYSIS/Tables/PartitionTrips.4.Rds")

colnames(partition_meals) <- c("Variable, Meals", "Mapping, Meals", "Information, Meals")
colnames(partition_trips) <- c("Variable, Trips", "Mapping, Trips", "Information, Trips")

xtable(partition_meals,
                               #digits = c(0, 0, 1, 1, 0, 0),
          caption = "Partition of outcomes, Meals"
          #align = "lmmm"
          )
#print(partition_meals, include.rownames = FALSE)

xtable(partition_trips,
                               #digits = c(0, 0, 1, 1, 0, 0),
          caption = "Partition of outcomes, Trips"
          #align = "lmmm"
          )
print(partition_meals, partition_trips, include.rownames = FALSE)
@
